Eye-tracking on the web: lessons learned from replicating 5 experiments

### 2022-05-09 manuscript.Rmd
Some initial elaboration of the Introduction.

*Present work*

In the present work, we attempted to replicate five eye-tracking studies
from the cognitive science literature using the eye-tracking plug-in
from `jsPsych`, a Javascript library for running behavioral experiments
in a web browser [@deleeuwJsPsychJavaScriptLibrary2015]. The plug-in
relies on the `webgazer.js` library for webcam eye-tracking
[@papoutsaki2016webgazer]. The goal was to examine the strengths and
weaknesses of webcam eye-tracking for common paradigms in cognitive
science. The studies were chosen to cover a variety of topic areas
(e.g., memory, decision-making, psycholinguistics) and paradigms (two
halves of the screen, visual world paradigm with four quadrants, visual
world paradigm with "natural" scenes). ...

@@

>>>>

# Present work

In order to validate online eyetracking measures, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms. The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science. Ideally, we would only attempt to replicate studies where the original measurements have small error bars and are known to replicate; otherwise, it can be difficult to distinguish a failure of the method (online eyetracking does not work) from a failure of the original study to replicate.

In practice, replications (successful or otherwise) have only been reported for a small number of studies, so we ultimately included some studies with unknown replicability. We addressed this in several ways. First, replicating five very different studies from different research traditions decreases our reliance on any one study. Second, we include several ``sanity check'' analyses, such as the correlation between calibration accuracy and effect size. (If the effect is real but there is noise from low-accuracy eyetracking, this correlation should be substantial.) Third, for XXX of the studies, we had comparison data collected in-lab either using jsPsych or a more traditional eyetracker technology, allowing us to direct assess the impact of differences in subject population and equipment.

## Selection of Studies

We chose five high-impact eyetracking studies involve adult subjects. (Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include exempars from a range of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two
halves of the screen, visual world paradigm with four quadrants, visual
world paradigm with "natural" scenes). As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.

The final selection of studies was FUBAR...

@@

In order to have adequate statistical power and precision, we aimed for XXXX participants per experiment.

## Equipment

We used a novel port of the `webgazer.js` library for webcam eyetracking [@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript library for running behavioral experiments
in a web browser [@deleeuwJsPsychJavaScriptLibrary2015]. We made several changes to webgazer.js in order to improve data quality. FUBAR
